\propertitle

### 2019-12-02 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-02T15:04:31+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

From these two assumptions the probability calculus allows us to calculate
the probability for the frequency distribution $\yF$ given the observed
frequency distribution for the sample $\yf$. The result is a mixture of
terms involving the joint frequencies of total activities of sample and
larger population $J_{\ya,\yA}$, multiplied by the number of time bins $T$:
\begin{equation}
  \label{eq:prob_joint_frequencies}
%\pxx[\yF \| \yf ] \propto
\prod_{\ya,\yA}\bigl(\yG_{\ya\yA}\;\nu_{\yA}\bigr)^{T\,J_{\ya,\yA}},
\end{equation}
with weights $q(\ynu)$, and with the marginal of the joint frequency
constrained Conditioning on the frequencies $\yf$ of the sample
would correspond to constraining the marginal
$\sum_{\yA}F_{\ya,\yA}=\yff_{\ya}$. The maximum-entropy method approximates
$T$ with infinity, thus treating the probability above as a delta. The
result is that
\begin{enumerate*}[label=(\roman*)]
\item the probability and observed frequency for the total activity $\yA$
  are constrained to be equal,
\item the frequency of sample activity $\ya$ conditional on
  larger-population activity $\yA$ is constrained to equal the
  hypergeometric distribution $\yG_{\ya\yA}$,
  \eqn~\eqref{eq:conditional_hypergeometric}.
\end{enumerate*}
Without this approximation the latter conditional frequency can differ from
$\yG_{\ya\yA}$, and this is expected if the number of bins $T$ is not much
larger than the number of possible joint possibilities, roughly
$n\times N$.

The final assumption in the maximum-entropy method regards the form of the
probability $\pxxx(\yA)$ in the expression above.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-12-02T17:12:16+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal population\\ from subpopulation data {\large\color{myred}[draft]}%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

From these two assumptions the probability calculus allows us to calculate
the probability $\pxx(\yF \| \yf )$ for the frequency distribution $\yF$
given the observed frequency distribution for the sample $\yf$. The result
is a mixture of terms involving the joint frequencies of total activities
of sample and larger population $J_{\ya,\yA}$, multiplied by the number of
time bins $T$:
\begin{equation}
  \label{eq:prob_joint_frequencies}
%\pxx[\yF \| \yf ] \propto
 \sum_{\bm{J}} \prod_{\ya,\yA}\bigl(\yG_{\ya\yA}\;\nu_{\yA}\bigr)^{T\,J_{\ya,\yA}}
  \qquad
  \text{with}\quad \tsum_{\yA}J_{\ya,\yA}=\yff_{\ya},
  \quad \tsum_{\ya}J_{\ya,\yA}=\yFF_{\yA},
\end{equation}
with weights $q(\ynu)$. The maximum-entropy method approximates $T$ with
infinity, thus treating the probability above as a delta. The result is
that
\begin{enumerate*}[label=(\roman*)]
\item the frequency distribution $\yF$ for the experiment and the long-run
  one $\ynu$ are constrained to be equal,
\item the frequency of the sample activity $\ya$ conditional on the
  larger-population activity $\yA$ is constrained to equal the
  hypergeometric distribution $\yG_{\ya\yA}$.
\end{enumerate*}
Without this approximation the latter conditional frequency can differ from
$\yG_{\ya\yA}$, and this is expected if the number of bins $T$ is not much
larger than the number of possible joint possibilities, roughly
$n\times N$.

The final assumption in the maximum-entropy method regards the form of the
probability $\pxx(\ynu)$ in the expressions above.
